---
title: "rafiki"
author: "rafiki"
date: "23 01 2021"
output: html_document
---

```{r}
library(tidyverse) # metapackage of all tidyverse packages
library(tokenizers)
library(stopwords)
library(tm)
library(text2vec)
library(fpc)
library(pdfCluster)
library(fossil)
```

```{r}
library(NbClust)
library(cluster)
library(factoextra)
library(dbscan)
```

# Wczytanie i przetworzenie danych


```{r}
data = read.csv("mbti_1.csv")
n <- 2000 #sample from data
labels <- c("ENFJ","ENFP","ENTJ","ENTP","ESFJ","ESFP",
            "ESTJ","ESTP","INFJ","INFP","INTJ","INTP",
            "ISFJ","ISFP","ISTJ","ISTP")

data <- data[sample(nrow(data), n), ]
```
```{r}
data[1,][2] 
```
```{r}
INTJ <- data[data$type=="INTJ",]
INTP <- data[data$type=="INTP",]
ENTJ <- data[data$type=="ENTJ",]
ENTP <- data[data$type=="ENTP",]
INFJ <- data[data$type=="INFJ",]
INFP <- data[data$type=="INFP",]
ENFJ <- data[data$type=="ENFJ",]
ENFP <- data[data$type=="ENFP",]
ISTJ <- data[data$type=="ISTJ",]
ISFJ <- data[data$type=="ISFJ",]
ESTJ <- data[data$type=="ESTJ",]
ESFJ <- data[data$type=="ESFJ",]
ISTP <- data[data$type=="ISTP",]
ISFP <- data[data$type=="ISFP",]
ESTP <- data[data$type=="ESTP",]
ESFP <- data[data$type=="ESFP",]

```

```{r}
#replaces URLs with word "link"
data$posts <- gsub('http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|(?:%[0-9a-fA-F][0-9a-fA-F]))+', 'link', data$posts)

#removes all noise from text
data$posts <- gsub('[^a-zA-Z]', " ", data$posts)

#removes more than 1 space
data$posts <- gsub('[ ]{2,}', " ", data$posts)

#word tokenization and stemming
data$posts <- tokenize_word_stems(data$posts, stopwords = stopwords::stopwords("en"))

#add column with cluster number(used to calculate rand index later on)
data_stats <- subset(data, select = c(type))
data_stats$cluster = match(data_stats$type, labels)

```

```{r}
#create dictionary
iterator = itoken(data$posts)
vocab = create_vocabulary(iterator)
pruned_vocab = prune_vocabulary(vocab, 
                                 term_count_min = 35, 
                                 doc_proportion_max = 0.7,
                                 doc_proportion_min = 0.1)
pruned_vocab
```

## Wektoryzacja

```{r}
#document term matrix
vectorizer = vocab_vectorizer(pruned_vocab)
dtm = create_dtm(iterator, vectorizer)

#(Term Co-occurrence Matrix)
tcm = create_tcm(iterator, vectorizer, skip_grams_window = 5L)

#tf_idf
tf_idf = TfIdf$new()
# fit tf-idf to training data
dt_tfidf = fit_transform(dtm, tf_idf)

# apply pre-trained tf-idf transformation to testing data
#doc_term_test_tfidf  = transform(doc_term_test, tf_idf)

vectors.dtm <- dtm
vectors.tfidf <- dt_tfidf
dim(dtm)
```

```{r}
glove = GlobalVectors$new(rank = 50, x_max = 10)
wv_main = glove$fit_transform(tcm, n_iter = 100, convergence_tol = 0.01, n_threads = 8)


wv_context = glove$components
word_vectors = wv_main + t(wv_context)

common_terms = intersect(colnames(dtm), rownames(word_vectors) )
dtm_averaged =  normalize(dtm[, common_terms], "l1")
sentence_vectors = dtm_averaged %*% word_vectors[common_terms, ]
vectors.glove <- sentence_vectors
```


```{r}
#split rows into single post not 50 
library(tidyr)
library(dplyr)

data2 = read.csv("mbti_1.csv")
data2 <- data2[sample(nrow(data2), 50), ]# do 200 jakoś idzie

#replaces URLs with word "link"
data2$posts <- gsub('http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|(?:%[0-9a-fA-F][0-9a-fA-F]))+', 'link', data2$posts)

data2 <-data2 %>% 
    mutate(posts = strsplit(as.character(posts), "\\|\\|\\|")) %>% 
    unnest(posts)

data2$posts <- gsub('[^a-zA-Z]', " ", data2$posts)

#removes more than 1 space
data2$posts <- gsub('[ ]{2,}', " ", data2$posts)

data2<-subset(data2, sapply(strsplit(posts, " "), length) >=8)

#word tokenization and stemming
data2$posts <- tokenize_word_stems(data2$posts, stopwords = stopwords::stopwords("en"))

#create dictionary
iterator2 = itoken(data2$posts)
vocab2 = create_vocabulary(iterator2)

pruned_vocab2 = prune_vocabulary(vocab2, 
                                 term_count_min = 5, 
                                 doc_proportion_max = 0.8,
                                 doc_proportion_min = 0.01)

data_stats2 <- subset(data2, select = c(type))
data_stats2$cluster = match(data_stats2$type, labels)

#document term matrix
vectorizer2 = vocab_vectorizer(pruned_vocab2)
dtm2 = create_dtm(iterator2, vectorizer2)
#(Term Co-occurrence Matrix)
tcm2 = create_tcm(iterator2, vectorizer2, skip_grams_window = 5L)



glove2 = GlobalVectors$new(rank = 50, x_max = 10)
wv_main2 = glove2$fit_transform(tcm2, n_iter = 100, convergence_tol = 0.01, n_threads = 8)


wv_context2 = glove2$components
word_vectors2 = wv_main2 + t(wv_context2)


common_terms = intersect(colnames(dtm2), rownames(word_vectors2) )
dtm_averaged =  normalize(dtm2[, common_terms], "l1")
sentence_vectors2 = dtm_averaged %*% word_vectors2[common_terms, ]
vectors.glove_post <- sentence_vectors2
```


# Grupowanie

```{r}
# metric = "euclidean", "manhattan", "gower"
manhattan.dtm <- daisy(as.matrix(vectors.dtm), metric = "manhattan")
manhattan.tfidf <- daisy(as.matrix(vectors.tfidf), metric = "manhattan")
manhattan.glove <- daisy(as.matrix(vectors.glove), metric = "manhattan")
manhattan.glove_post <- daisy(as.matrix(vectors.glove_post), metric = "manhattan")
```

```{r}
euclidean.dtm <- daisy(as.matrix(vectors.dtm), metric = "euclidean")
euclidean.tfidf <- daisy(as.matrix(vectors.tfidf), metric = "euclidean")
euclidean.glove <- daisy(as.matrix(vectors.glove), metric = "euclidean")
euclidean.glove_post <- daisy(as.matrix(vectors.glove_post), metric = "euclidean")
```
  
```{r}
gower.dtm <- daisy(as.matrix(vectors.dtm), metric = "gower")
gower.tfidf <- daisy(as.matrix(vectors.tfidf), metric = "gower")
gower.glove <- daisy(as.matrix(vectors.glove), metric = "gower")
gower.glove_post <- daisy(as.matrix(vectors.glove_post), metric = "gower")
```

## Grupowanie Hierarchiczne

### DTM
## complete

```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.dtm, k = 16, hc_method = "complete")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.dtm,ellipse.type = "convex")
```
```{r}
ran_comp <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



pam_results <- subset(ran_comp, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(pam_results$cluster), data_stats$cluster)
adj.rand.index(pam_results$cluster, data_stats$cluster)
cluster.stats(euclidean.dtm, pam_results$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

## mcquitty

```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.dtm, k = 16, hc_method = "mcquitty")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.dtm,ellipse.type = "convex")
```
```{r}
ran_comp <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



pam_results <- subset(ran_comp, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(pam_results$cluster), data_stats$cluster)
adj.rand.index(pam_results$cluster, data_stats$cluster)
cluster.stats(euclidean.dtm, pam_results$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

## euclidean

```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.dtm, k = 16, hc_method = "ward.D2")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.dtm,ellipse.type = "convex")
```
```{r}
ran_comp <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



pam_results <- subset(ran_comp, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(pam_results$cluster), data_stats$cluster)
adj.rand.index(pam_results$cluster, data_stats$cluster)
cluster.stats(euclidean.dtm, pam_results$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

### TfIDF

## complete

```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.tfidf, k = 16, hc_method = "complete")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.tfidf,ellipse.type = "convex")
```
```{r}
ran_comp <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



pam_results <- subset(ran_comp, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(pam_results$cluster), data_stats$cluster)
adj.rand.index(pam_results$cluster, data_stats$cluster)
cluster.stats(euclidean.tfidf, pam_results$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

## mcquitty

```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.tfidf, k = 16, hc_method = "mcquitty")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.tfidf,ellipse.type = "convex")
```
```{r}
ran_comp <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



pam_results <- subset(ran_comp, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(pam_results$cluster), data_stats$cluster)
adj.rand.index(pam_results$cluster, data_stats$cluster)
cluster.stats(euclidean.tfidf, pam_results$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

## ward.D2

```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.tfidf, k = 16, hc_method = "ward.D2")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.tfidf,ellipse.type = "convex")
```
```{r}
ran_comp <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



pam_results <- subset(ran_comp, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(pam_results$cluster), data_stats$cluster)
adj.rand.index(pam_results$cluster, data_stats$cluster)
cluster.stats(euclidean.tfidf, pam_results$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

### GLOVE


## complete
```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.glove, k = 16, hc_method = "complete")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.glove,ellipse.type = "convex")
```

```{r}
hc.cut.res <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
cluster.stats(euclidean.glove, hc.cut.g.res$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```
## mcquitty
```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.glove, k = 16, hc_method = "mcquitty")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.glove,ellipse.type = "convex")
```

```{r}
hc.cut.res <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
cluster.stats(euclidean.glove, hc.cut.g.res$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

## ward d2
```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.glove, k = 16, hc_method = "ward.D2")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.glove,ellipse.type = "convex")
```

```{r}
hc.cut.res <- data %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
cluster.stats(euclidean.glove, hc.cut.g.res$cluster, alt.clustering=data_stats$cluster)$avg.silwidth
```

### GLOVE Posts

## complete
```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.glove_post, k = 16, hc_method = "complete")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.glove_post,ellipse.type = "convex")
```

```{r}
hc.cut.res <- data2 %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(hc.cut.g.res$cluster), data_stats2$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats2$cluster)
cluster.stats(euclidean.glove_post, hc.cut.g.res$cluster, alt.clustering=data_stats2$cluster)$avg.silwidth
```
## mcquitty
```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.glove_post, k = 16, hc_method = "mcquitty")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.glove_post,ellipse.type = "convex")
```

```{r}
hc.cut.res <- data2 %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(hc.cut.g.res$cluster), data_stats2$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats2$cluster)
cluster.stats(euclidean.glove_post, hc.cut.g.res$cluster, alt.clustering=data_stats2$cluster)$avg.silwidth
```

## ward d2
```{r}
# Use hcut() which compute hclust and cut the tree
# rownames(dissimilarity.tfidf) <- rownames(data$type)
hc.cut <- hcut(euclidean.glove_post, k = 16, hc_method = "ward.D2")
# Visualize dendrogram
# fviz_dend(hc.cut, show_labels = FALSE, rect = TRUE)
# Visualize cluster

```
```{r}
fviz_cluster(hc.cut, data = euclidean.glove_post,ellipse.type = "convex")
```

```{r}
hc.cut.res <- data2 %>%
mutate(cluster = hc.cut$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
rand.index(unname(hc.cut.g.res$cluster), data_stats2$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats2$cluster)
cluster.stats(euclidean.glove_post, hc.cut.g.res$cluster, alt.clustering=data_stats2$cluster)$avg.silwidth
```


## DBSCAN



### DTM
## euclidean
Należy odczytać gdzie na wykresie jest tak zwanne kolano, czyli punkt, po którym wykres zaczyna ustawiać się w pionie. Wartość tego punktu zostaje zastosowana jako eps.
```{r}
kNNdistplot(euclidean.dtm, k = 10)

```

```{r}
eps = 30
dbscan_res <- fpc::dbscan(euclidean.dtm, eps = eps, MinPts = 10, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = euclidean.dtm)
```
```{r}
hc.cut.res <- data %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
```
## Manhatan
```{r}
kNNdistplot(manhattan.dtm, k = 2)

```

```{r}
eps = 400
dbscan_res <- fpc::dbscan(manhattan.dtm, eps = eps, MinPts = 2, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = manhattan.dtm)
```
```{r}
hc.cut.res <- data %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
```
### TFID
## euclidean
Należy odczytać gdzie na wykresie jest tak zwanne kolano, czyli punkt, po którym wykres zaczyna ustawiać się w pionie. Wartość tego punktu zostaje zastosowana jako eps.
```{r}
kNNdistplot(euclidean.tfidf, k = 2)

```

```{r}
eps = 0.19
dbscan_res <- fpc::dbscan(euclidean.tfidf, eps = eps, MinPts = 2, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = euclidean.tfidf)
```
```{r}
hc.cut.res <- data %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
```
## Manhatan
```{r}
kNNdistplot(manhattan.tfidf, k = 2)

```

```{r}
eps = 2.2
dbscan_res <- fpc::dbscan(manhattan.tfidf, eps = eps, MinPts = 2, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = manhattan.tfidf)
```
```{r}
hc.cut.res <- data %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
```
### GLOVE

## manhattan
Należy odczytać gdzie na wykresie jest tak zwanne kolano, czyli punkt, po którym wykres zaczyna ustawiać się w pionie. Wartość tego punktu zostaje zastosowana jako eps.
```{r}
kNNdistplot(manhattan.glove, k = 2)

```

```{r}
eps = 3
dbscan_res <- fpc::dbscan(manhattan.glove, eps = eps, MinPts = 2, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = manhattan.glove)
```
```{r}
hc.cut.res <- data %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
```

## euclidean
```{r}
kNNdistplot(euclidean.glove, k = 2)

```

```{r}
eps = 0.4
dbscan_res <- fpc::dbscan(euclidean.glove, eps = eps, MinPts = 2, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = euclidean.glove)
```
```{r}
hc.cut.res <- data %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats$cluster)
```
### GLOVE POST
## manhattan

Należy odczytać gdzie na wykresie jest tak zwanne kolano, czyli punkt, po którym wykres zaczyna ustawiać się w pionie. Wartość tego punktu zostaje zastosowana jako eps.
```{r}
kNNdistplot(manhattan.glove_post, k = 2)

```

```{r}
eps = 8
dbscan_res <- fpc::dbscan(manhattan.glove_post, eps = eps, MinPts = 2, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = manhattan.glove_post)
```
```{r}
hc.cut.res <- data2 %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats2$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats2$cluster)
cluster.stats(manhattan.glove_post, hc.cut.g.res$cluster, alt.clustering=data_stats2$cluster)$avg.silwidth
```
## Euclidean
```{r}
kNNdistplot(euclidean.glove_post, k = 2)

```

```{r}
eps = 1.5
dbscan_res <- fpc::dbscan(euclidean.glove_post, eps = eps, MinPts = 2, method="dist")
```
```{r}
fviz_cluster(dbscan_res, data = euclidean.glove_post)
```
```{r}
hc.cut.res <- data2 %>%
mutate(cluster = dbscan_res$cluster) %>%
group_by(cluster)



hc.cut.g.res <- subset(hc.cut.res, select = c(type, cluster))
#calculate stats and rand index
table(hc.cut.g.res)
```
```{r}
rand.index(unname(hc.cut.g.res$cluster), data_stats2$cluster)
adj.rand.index(hc.cut.g.res$cluster, data_stats2$cluster)
cluster.stats(euclidean.glove_post, hc.cut.g.res$cluster, alt.clustering=data_stats2$cluster)$avg.silwidth
```

